Life in the canopy: community trait assessments reveal substantial functional diversity among fern epiphytes

### 2019-12-28 ms/manuscript.Rmd
Don't use knitr cache

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)
library(drake)
library(gt)
library(patchwork)
library(knitr)
library(kableExtra)
library(magrittr)
library(scales)
library(tidyverse)
library(conflicted)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE)
library(drake)
library(gt)
library(patchwork)
library(knitr)
library(kableExtra)
library(magrittr)
library(scales)
library(tidyverse)
library(conflicted)
